Algorithm explanation

### 2013-09-25 article/interpolation.tex
Stash

Among various program verification techniques, when software model
checking with predicate abstraction is adopted, the interpolation is
used to compute the abstraction predicate along a spurious
counterexample that a model checker discovered.  It is done by
computing a Craig interpolant between the strongest postcondition at
the location and the weakest precondition to the failure point at
every program location.

>>>>

Among various program verification techniques, the interpolation has
been used to extract a program behavior as a logical formula.
Especially when one adopts software model checking technique with
predicate abstraction, the interpolation computes the abstraction
predicate along a spurious counterexample that a model checker
discovered.

It is done by computing a logical separation between the strongest
postcondition at the location and the weakest precondition to the
failure point at every program location.
